Exposing Bugs in JavaScript Engines through Test Transplantation and Differential Testing

### 2020-06-12 paper/paper.tex
First pass on Sections 7 and 8

\vspace{1ex}\noindent\textbf{Issue \#35, Table~\ref{tab:test-transplantation-bugs}.} We
reported the snippet \CodeIn{"use strict" 010} to the
\textbf{\smonkey} development team as a bug and the bug was confirmed
in a few hours.  This is a test case original from the \hermes suite
using test transplantation.  According the specification, in strict
mode, the engine must use the prefix '0o' or '0O' to represents octal
numeric literals. It was an issue which explores a deprecated octal
token after ASI (Automatic Semicolon Insertion).  The others engine
throws a SyntaxError due the missing of the octal token, but \smonkey
returns a integer 8 that represents 010 in octal.

@@

\vspace{1ex}\noindent\textbf{Issue \#24, Table~\ref{tab:bugs}.} The snippet
\CodeIn{b+/v/a} represents a bug confirmed in \hermes\ engine with
differential testing using radamsa on a repository mined from GitHub.
The original test case contains a string concatenation.
This is a case of validation of RegExp flags. The fuzzer mutates
the file with a regular expression \CodeIn{/v/} after the plus operator.
In this case, the plus operator turns into a flag of the RegExp \CodeIn{+/v/},
but this flag is not valid. The behavior expected is throws an early
SyntaxError due to a invalid regular expression flag,
but \hermes\ seems not treats the early validation of the regexp flags
as commented by a maintainer.

>>>>

\vspace{1ex}\noindent\textbf{Issue \#35, Table~\ref{tab:test-transplantation-bugs}.} We
reported the snippet \CodeIn{"use strict" 010} to the
\textbf{\smonkey} development team as a bug and the bug was confirmed
in a few hours.  This is a test case originally from the \hermes suite
using test transplantation.  According the specification, in strict
mode, the engine must use the prefix '0o' or '0O' to represent octal
numeric literals. This is an issue that explores a deprecated octal
token after ASI (Automatic Semicolon Insertion). The other engines
throw a SyntaxError due to the missing of the octal token, but \smonkey
returns an integer \CodeIn{8} that represents \CodeIn{010} in octal.

@@

\vspace{1ex}\noindent\textbf{Issue \#24, Table~\ref{tab:bugs}.} The snippet
\CodeIn{b+/v/a} represents a bug confirmed in \textbf{\hermes} engine with
differential testing using radamsa on a repository mined from GitHub.
The original test case contains a string concatenation.
This is a case of validation of RegExp flags. The fuzzer mutates
the file with a regular expression \CodeIn{/v/} after the plus operator.
In this case, the plus operator turns into a flag of the RegExp \CodeIn{+/v/},
but this flag is not valid. The expected behavior is to throw an early
SyntaxError due to the invalid regular expression flag,
but \hermes\ seems not to treat the early validation of the regexp flags
as commented by a maintainer.
